I am grateful for my time at Campus Drie Eiken, and wholeheartedly enjoyed being around for so long.
In all the research groups which accommodated me, I was welcomed with a supportive, friendly, collaborative, and creative atmosphere, which is all due to the great people I met there.

\bigskip
As seems to be the nature of these things, my project took a bit longer, and so I saw many fellow students and researchers leave, and others join.
I am glad to have met all of you inspiring, young and creative people, and I wish each of you all the best!
I will not attempt to list all of you PhD students and postdocs, nor will I pick individuals.
The reasons are your sheer number (three different departments!), an approaching print deadline, and the fear of missing any important person.
And I am humbled by those of you who did take or will take the time to write individual acknowledgements, how cool is that?

Kudos, my friends! Keep on the great research!

\medskip
However, I must point out my ``office roommates'': Miriam Ayuso Hernando, Lieselotte Van Bockstal, Sara Prims, Joaquim Sanctorum, Simon Baeckens, and Maja Mielke.
Thank you for being mild (or at least pretending to not care about) my chaotic desks and loud keyboards.


\bigskip
A special shout-out to the phenomenal technical and administrative support staff for whom I caused a lot of work: Katty Huybrechts, Gunther Vrolix, Steve Van Bienst, Josie Meaney-Ward, Jan Scholliers and Jorrit Mertens.
I appreciate your great efforts and your open ear to my problems and frustrations.
In contrast to some other ``supportive'' and ``administrative'' departments, you were actually and personally there, and oftentimes I would have been lost without you.
You are who keep the labs running -- modern pastoral care, in a world full of compliance bullshit and supply chain crackdowns.
Thank you!

Also a technical staff by now, and a great support, I am thankful for the brief period I teamed up with Joaquim Sanctorum to operate the ``DynXLab''.
I am glad that you took it into your able hands, and wish you all the best, there or elsewhere!


\bigskip
I wave my virtual hand and bow to the participants of our virtual COVID Coffee Club, the ``UA Code Clinic'', the 2019 research day committee, and regular TGIF guests; we should do all that again!
And I am glad that the ``Vrienden van de Ark'', the caretakers (mainly Denise, An, Ellen), and Harlee were there to teach me various cool skills such as handling cows, taking a Lama's temperature, or how to operate a ``potstall''.
Matter of fact, I enjoyed ``arkdienst'', and occasionally have to force myself to think about that monstrous dung heap, to counteract a wistful memory creeping in.


\bigskip
None of my studies and research, as meaningless as they might be, would not have been possible without the inspiring work of Alexandra Elbakyan (sci-hub) and the developers of ``yt-dlp''.
There are a tremendous number of people who depend on your enormous efforts, and think that you deserve all our thanks and praises for your courage.


\bigskip
A collegial ``Thank You!'' to all the reviewers who took time to read and improve my often cryptic or technical texts.
And, not less, one to those reviewers who did not care or did not have time, and just let me pass.
I appreciate the efforts of all my jury members: I was struggling in my pre-defence, yet in a good way, and the reason is that all of you took the time to carefully assess my lengthy research reports.
I acknowledge that I am not the most ``readable'' writer, and thus I much appreciate your efforts and feedback, thank you!



\bigskip
There is one special person to fit many of the above categories.
Of course, I mean Sam Van Wassenbergh, who, besides other roles, is a professor and still has at least half a foot in D-1.39.
\begin{quote}
\textit{Do not be too sad, Sam.
You cannot always be torn in two.
You will have to be one and whole, for many years.
You have so much to enjoy and to be, and to do. }
\end{quote}
It was not quite ``Mount Doom'', but I remember us standing in the fully prepared recording room, a foot deep in water, between a high-voltage closet, a self-soldered ``trogger'' (shorthand for ``Trigger-Logger'', an add-on device necessary because the force plate recordings would require all of my computer's capacity), and a unique piece of Jan's phenomenal balsa wood craftsmanship.
Someone had removed a critical pump, and our x-ray room was a swimming pool.
It must have been a nightmare come true.
Yet we focused. We cleaned up. And we made it.
Thank you so much!


\bigskip
I will not forget my supervisors!

Chris.
You protected me when I was threatened with administrative punishment (e.g. ``no show arbeidsarts'') or disaster (e.g. ``gelijkstelling FELASA'').
I wholeheartedly thank you for the more memorable (computer-free) days of my PhD, involving unforgettable trips to remote farms full of farrowing sows, or the scanning of a giraffe skeleton.
By far the most memorable event was a trip to the zoo; I am so glad that I was allowed to join.
You were always there with sharp wits; you showed an incredible stamina to read texts which were full of jargon from other fields, and nonetheless you saved me from many misformulations and mistakes.
You are a great person, and a role model, and I wish you all thinkable luck and success for the possible new role as vice rector, or any other challenge you take beside or beyond it!

Peter.
For some reason, I feel that we had a bumpy start on the professional side, which involved several occasions where we would exchange page-long mails (sorry!) or hold intense discussions for hours (``referentierooster''!).
Then we would usually clarify some basic terminology to find out that we are actually on the same page.
I must take those on me, because by now I got to know you as a knowledgeable, generous and patient supervisor; I enjoy our scientific discussions and hope that we will have many more chances.
I am sorry for the one or the other night which you might have been awake contemplating one or the other dead end of this project.
\ldots{}or my incapability to obey university rules and authorities (e.g. ``opleidingskrediet'', ``edumaster enrolment'').
And I admire your attitude to climb the attic to convince me that fictitious forces don't exist (or, do they?), to write very useful code (though personally I would never choose Matlab), and to keep on pursuing the flamingo project.
I sincerely hope that we do not ``loose'' you to pension, but ``win'' you time for the fun research projects which have been lingering in the back of your head (if you like).
Enjoy, anyways, and all the best for it!

Both of you have found a good mode to manage the more Don-Quijote-like aspects of my personality, supportive when it was adequate, always fair and reasonable; for that I am glad.
I could not have wished for better supervisors.



\newpage
Finally, I am full of love and thankfulness for the support of my family.
Maja, Mona, Ronja, my parents, grandparents, (grand)parents in law; all my direct and acquired siblings and their families; with special mention of Alex, Andreza, and Leonardo.
I think that the more personal appreciation is best shared in person (another good reason to meet more often).
Thank you!
I hope to see you all, soon.

Nevertheless, the final words must be dedicated to Maja, who, besides being my wife and friend and lover and the best possible mother for our kids and everything I could ever wish to find in a partner, also jumps in with professional advice on biomechanics, with an ear for my swearing, or just some of her time to keep the little troubles of life at distance.
Your contribution to this project is most invaluable, my dear.
Danke, dass Du bei mir bist!
